Time stability in human interaction networks

### 2015-06-06 paper.tex
finished bibliography corrections

\begin{figure}
   \centering
        \includegraphics[width=\columnwidth]{figs/mpgamma____________}
	\caption{A scatter plot of messages (M) versus participants (N) versus threads ($\Gamma$) for 140 email lists. The highest number of threads are found in lists with few participants. The correlation between $N$ and $\Gamma$ is negative for low values of $N$ but positive otherwise. This negative correlation between $N$ and $\Gamma$ can also be observed in Table~\ref{tab:genLists}. For $M=20000$ messages, positive correlation of $N$ and $\Gamma$ is present mostly above 1500 participants. All LAU, LAD, MET lists present smaller networks.}
	\label{fig:nmgamma3d}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section*{APPENDIX: Data and scripts}\label{scripts}
Messages were downloaded from the GMANE public database~\cite{GMANEwikipedia}. Data annotated from Facebook and Twitter are in a public repository~\ref{fbtwData}. Data from Participa.br was used from the linked data/semantic web RDF triples available in~\cite{rdfParticipa}.
All routines necessary to achieve the results reported in this article, including all tables and figure of the Supporting Information, are available through a public domain Python package and an open Git repository~\cite{gmanePack}.

>>>>

\begin{figure}
   \centering
        \includegraphics[width=\columnwidth]{figs/mpgamma____________}
	\caption{A scatter plot of messages (M) versus participants (N) versus threads ($\Gamma$) for 140 email lists. Highest number of threads are found in lists with few participants. The correlation between $N$ and $\Gamma$ is negative for low values of $N$ but positive otherwise. This negative correlation between $N$ and $\Gamma$ can also be observed in Table~\ref{tab:genLists}. For $M=20000$ messages, positive correlation of $N$ and $\Gamma$ is present mostly above 1500 participants. All LAU, LAD, MET lists present smaller networks.}
	\label{fig:nmgamma3d}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section*{APPENDIX: Data and scripts}\label{scripts}
Messages were downloaded from the GMANE public database~\cite{GMANEwikipedia}. Data annotated from Facebook and Twitter are in a public repository~\cite{fbtwData}. Data from Participa.br was used from the linked data/semantic web RDF triples reported in~\cite{opa} and available in~\cite{datahub}.
All routines necessary to achieve the results reported in this article, including all tables and figure of the Supporting Information, are available through a public domain Python package and an open Git repository~\cite{gmanePack}. Data from social networks used in this study were gathered and used within the Anthropological Physics principles~\cite{anPhy}.
